Digital History in Finland, 1488-1828

### 2016-07-01 inst/examples/manuscript-krakow.Rmd
ok

@@

```{r publishers3-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=10}
# Title count
catalogue <- "Fennica"
place <- "Turku"

@@

theme_set(theme_bw(20))
p <- ggplot(npub, aes(x = publication_decade, y = n)) +
       geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
       #geom_point(size = 5, aes(shape = publisher)) +
       #geom_line(col = "black", aes(shape = publisher)) +       
       # geom_smooth(col = "black", aes(shape = publisher)) + 
       xlab("Publication year") +
       ylab("Title count (n)") +        
       ggtitle(paste("Title count (", place, "/", catalogue, ")", sep = ""))
print(p)

@@

theme_set(theme_bw(20))
p <- ggplot(npub, aes(x = publication_decade, y = paper)) +
       geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
       #geom_point(size = 5, aes(shape = publisher)) +
       #geom_line(col = "black", aes(shape = publisher)) +       
       # geom_smooth(col = "black", aes(shape = publisher)) + 
       xlab("Publication year") +
       ylab("Paper") +        
       ggtitle(paste("Paper (", place, "/", catalogue, ")", sep = ""))
print(p)

>>>>

Number of unique publishers in top publication places over time:

@@

Title count per top publisher (two alternative visualizations):

```{r publishers3-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
# Title count
catalogue <- "Fennica"
place <- "Turku"

@@

theme_set(theme_bw(20))
p <- ggplot(npub, aes(x = publication_decade, y = n)) +
       geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
       #geom_point(size = 5, aes(shape = publisher)) +
       #geom_line(col = "black", aes(shape = publisher)) +       
       # geom_smooth(col = "black", aes(shape = publisher)) + 
       xlab("Publication year") +
       ylab("Title count (n)") +        
       ggtitle(paste("Title count (", place, "/", catalogue, ")", sep = ""))
print(p)
```

Paper consumption per top publisher (two alternative visualizations):

```{r publishers4-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}

@@

theme_set(theme_bw(20))
p <- ggplot(npub, aes(x = publication_decade, y = paper)) +
       geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
       #geom_point(size = 5, aes(shape = publisher)) +
       #geom_line(col = "black", aes(shape = publisher)) +       
       # geom_smooth(col = "black", aes(shape = publisher)) + 
       xlab("Publication year") +
       ylab("Paper") +        
       ggtitle(paste("Paper (", place, "/", catalogue, ")", sep = ""))
print(p)
```
